>

### 2020-09-22 manuscript/manuscript.Rmd
Make graphic with tikz

```{r map, fig.env="figure*", echo=FALSE, message=FALSE, warning=FALSE, fig.height=4, fig.cap="Normalized utility-based park accessibility values in New York City."}
library(ggmap)
map <- ggmap(
  get_stamenmap(unname(st_bbox(tracts)), 
                maptype = "toner-lite"), extent = "device")
map +
  geom_sf(data = tracts, inherit.aes=FALSE,
          aes(fill = cut(euc_multi, breaks = c(-Inf, -3, -2, -1, 0, 1, 2, 3, Inf))),
          alpha = 0.9, color = NA) +
  scale_fill_brewer("Accessibility", palette = "RdYlBu")
```

>>>>

```{r map, fig.env="figure*", echo=FALSE, message=FALSE, warning=FALSE, fig.height=4, fig.cap="Normalized utility-based park accessibility values in New York City.", dev='tikz'}
library(ggmap)
map <- ggmap(
  get_stamenmap(unname(st_bbox(tracts)), 
                maptype = "toner-lite"), extent = "device")
map +
  geom_sf(data = tracts, inherit.aes=FALSE,
          aes(fill = cut(euc_multi, breaks = c(-Inf, -3, -2, -1, 0, 1, 2, 3, Inf))),
          alpha = 0.9, color = NA) +
  scale_fill_brewer("Accessibility", palette = "RdYlBu")
```
